Multi-reference pangenome graphs

### 2022-01-08 manuscript/fig_induction.tex
get the first figure in
not like this

\documentclass{article}
\usepackage{tikz}
\usepackage{comment}
\usetikzlibrary{positioning}

@@

\begin{document}
\begin{tikzpicture}[auto,
    node distance= 10mm and 20mm,
    font=\sffamily,
    roundnode/.style={circle, draw=black!60, fill=gray!10, very thick, minimum size=7mm},
    squarednode/.style={rectangle, draw=black!60, fill=gray!10, very thick, minimum size=5mm},
    graphnode/.style={rectangle, draw=black!60, fill=black!100, text=white, very thick, minimum size=5mm},
    keynode/.style={rectangle, draw=black!60, fill=gray!10, thick, minimum size=1mm}
    %draw matchclosure/.style={very thick,color=gray!100}
]
%Nodes
\node[squarednode,label=left:text1] (seqA1) {G};
\node[squarednode] (seqA2) [right of=seqA1] {A};
\node[squarednode] (seqA3) [right of=seqA2] {T};
\node[squarednode] (seqA4) [right of=seqA3] {T};
\node[squarednode] (seqA5) [right of=seqA4] {A};
\node[squarednode] (seqA6) [right of=seqA5] {C};
\node[squarednode] (seqA7) [right of=seqA6] {A};

@@

%Lines
\draw[very thick] (seqA1) -- (seqA2);
\draw[very thick] (seqA2) -- (seqA3);
\draw[very thick] (seqA3) -- (seqA4);
\draw[very thick] (seqA4) -- (seqA5);
\draw[very thick] (seqA5) -- (seqA6);
\draw[very thick] (seqA6) -- (seqA7);

\draw[very thick] (seqB1) -- (seqB2);
\draw[very thick] (seqB2) -- (seqB3);
\draw[very thick] (seqB3) -- (seqB4);
\draw[very thick] (seqB4) -- (seqB5);
\draw[very thick] (seqB5) -- (seqB6);
\draw[very thick] (seqB6) -- (seqB7);

\draw[very thick] (seqC1) -- (seqC2);
\draw[very thick] (seqC2) -- (seqC3);
\draw[very thick] (seqC3) -- (seqC4);
\draw[very thick] (seqC4) -- (seqC5);

@@

@@

%\draw[->] (uppercircle.south) -- (seq1.north);
%\draw[->] (seq1.east) -- (rightsquare.west);
%\draw[->] (rightsquare.south) .. controls +(down:7mm) and +(right:7mm) .. (lowercircle.east);
%\draw[->] (rightsquare.south) -- (lowercircle.east);
\end{tikzpicture}
\end{document}

>>>>

\documentclass[tikz,margin=0pt]{standalone}

%\setlength{\paperwidth}{108mm}
%\setlength{\paperheight}{210mm}
%\ifx\pdfoutput\undefined
%\else
%\setlength{\pdfpagewidth}{\paperwidth}
%\setlength{\pdfpageheight}{\paperheight}
%\fi

%\usepackage{tikz}
\usepackage{comment}
\usetikzlibrary{positioning}

@@

\begin{document}
\begin{tikzpicture}[auto,
    node distance= 10mm and 20mm,
    font=\sffamily,
    roundnode/.style={circle, draw=black!60, fill=gray!10, very thick, minimum size=7mm},
    squarednode/.style={rectangle, draw=black!60, fill=gray!10, very thick, minimum size=5mm},
    graphnode/.style={rectangle, draw=black!60, fill=black!100, text=white, very thick, minimum size=5mm},
    keynode/.style={rectangle, draw=black!60, fill=gray!10, thick, minimum size=1mm},
    pathnode/.style={rectangle, minimum size=5mm},
    %draw matchclosure/.style={very thick,color=gray!100}
]
%Nodes
\node[squarednode,label=left:text1] (seqA1) {G};
\node[squarednode] (seqA2) [right of=seqA1] {A};
\node[squarednode] (seqA3) [right of=seqA2] {T};
\node[squarednode] (seqA4) [right of=seqA3] {T};
\node[squarednode] (seqA5) [right of=seqA4] {A};
\node[squarednode] (seqA6) [right of=seqA5] {C};
\node[squarednode] (seqA7) [right of=seqA6] {A};

@@

%Lines
\draw[very thick,color=red] (seqA1) -- (seqA2);
\draw[very thick,color=red] (seqA2) -- (seqA3);
\draw[very thick,color=red] (seqA3) -- (seqA4);
\draw[very thick,color=red] (seqA4) -- (seqA5);
\draw[very thick,color=red] (seqA5) -- (seqA6);
\draw[very thick,color=red] (seqA6) -- (seqA7);

\draw[very thick,color=green] (seqB1) -- (seqB2);
\draw[very thick,color=green] (seqB2) -- (seqB3);
\draw[very thick,color=green] (seqB3) -- (seqB4);
\draw[very thick,color=green] (seqB4) -- (seqB5);
\draw[very thick,color=green] (seqB5) -- (seqB6);
\draw[very thick,color=green] (seqB6) -- (seqB7);

\draw[very thick,color=blue] (seqC1) -- (seqC2);
\draw[very thick,color=blue] (seqC2) -- (seqC3);
\draw[very thick,color=blue] (seqC3) -- (seqC4);
\draw[very thick,color=blue] (seqC4) -- (seqC5);

@@

\node[pathnode,label=left:path1] (pathA1) [below = 1cm of g1] {1};
\node[pathnode] (pathA2) [right of=pathA1] {2};
\node[pathnode] (pathA3) [right of=pathA2] {3};
\node[pathnode] (pathA4) [right of=pathA3] {4};
\node[pathnode] (pathA5) [right of=pathA4] {5};
\node[pathnode] (pathA6) [right of=pathA5] {6};
\node[pathnode] (pathA7) [right of=pathA6] {7};

\node[pathnode,label=left:path2] (pathB1) [below of=pathA1] {1};
\node[pathnode] (pathB2) [right of=pathB1] {8};
\node[pathnode] (pathB3) [right of=pathB2] {3};
\node[pathnode] (pathB4) [right of=pathB3] {4};
\node[pathnode] (pathB5) [right of=pathB4] {5};
\node[pathnode] (pathB6) [right of=pathB5] {6};
\node[pathnode] (pathB7) [right of=pathB6] {9};

\node[pathnode,label=left:path3] (pathC1) [below of=pathB1] {1};
\node[pathnode] (pathC2) [right of=pathC1] {2};
\node[pathnode] (pathC3) [right of=pathC2] {3};
\node[pathnode] (pathC4) [below of=pathB6] {6};
\node[pathnode] (pathC5) [right of=pathC4] {7};

\draw[very thick] (pathA1) -- (pathA2);
\draw[very thick] (pathA2) -- (pathA3);
\draw[very thick] (pathA3) -- (pathA4);
\draw[very thick] (pathA4) -- (pathA5);
\draw[very thick] (pathA5) -- (pathA6);
\draw[very thick] (pathA6) -- (pathA7);

\draw[very thick] (pathB1) -- (pathB2);
\draw[very thick] (pathB2) -- (pathB3);
\draw[very thick] (pathB3) -- (pathB4);
\draw[very thick] (pathB4) -- (pathB5);
\draw[very thick] (pathB5) -- (pathB6);
\draw[very thick] (pathB6) -- (pathB7);

\draw[very thick] (pathC1) -- (pathC2);
\draw[very thick] (pathC2) -- (pathC3);
\draw[very thick] (pathC3) -- (pathC4);
\draw[very thick] (pathC4) -- (pathC5);

@@

%\draw[->] (uppercircle.south) -- (seq1.north);
%\draw[->] (seq1.east) -- (rightsquare.west);
%\draw[->] (rightsquare.south) .. controls +(down:7mm) and +(right:7mm) .. (lowercircle.east);
%\draw[->] (rightsquare.south) -- (lowercircle.east);
\end{tikzpicture}

\end{document}
